Digital History in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
top authors

---
title: "Paper Consumption in Finland, 1488-1828"
author: "Niko Ilomäki"
date: "December 7, 2015"
output: markdown_document
---

@@

# Read data
df <- readRDS("df.Rds")

# Let us focus on years 1400-1828
df <- df %>% filter(publication_year > 1400 & publication_year < 1829)

# Add publication decade
# TODO add already in the original preprocessed data matrix
df$publication_decade <- 10*floor(df$publication_year/10)
```

@@

@@

#p + guides(fill = guide_legend(order = 1))

```

>>>>

---
title: "Digital History in Finland, 1488-1828"
author: "Leo Lahti"
date: "December 9, 2015"
output: markdown_document
---

This markdown document contains presentation material for [Digital History in Finland seminar (University of Helsinki, Dec 9, 2015)](http://blogs.helsinki.fi/mstolone/2015/09/21/call-for-papers-digital-history-in-finland-wednesday-9-12-2015/). The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/rOpenGov/fennica/blob/master/inst/examples/20151209-HelsinkiDH.md).

@@

# Read data
dfo <- readRDS("df.Rds")

# Add publication decade
# TODO add already in the original preprocessed data matrix
dfo$publication_decade <- 10*floor(dfo$publication_year/10)

# Remove very early and late years
dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)
```

@@

# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829)

@@

#p + guides(fill = guide_legend(order = 1))
```

```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))

p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))

library(gridExtra)
grid.arrange(p1, p2, nrow = 1)
```
